---
title: "Final data preprocessing and EAT score re-calculation"
author: "Miha Likar"
format:
  html:
    toc: true
    toc-depth: 4
    number-sections: true
    toc-expand: true
editor: visual

---

```{r}
library(tidyverse)
```

# Prepare name vectors and dictionary

Create vectors of items:
```{r}
mwq_items <- paste0("mwq_", c(1:5))
mssb_items <- paste0("MSSB_", c(1:38))
ocir_items <- paste0("OCI_R_", c(1:18))
aq_items <- paste0("AQ_", c(1:50))
asrs_items <- paste0("ASRS_", c(1:18))
bdi_items <- paste0("BDI_shorten_", c(1:9))
eat_items <- paste0("EAT_", c(1:26))
hcl_items <- paste0("HCL32_", c(1:32))
stai_trait_items <- paste0("STAI_trait_", c(21:40))
```

MSSB
```{r}
mssb_positive <- c(
  "MSSB_2",
  "MSSB_5",
  "MSSB_8",
  "MSSB_11",
  "MSSB_14",
  "MSSB_17",
  "MSSB_20",
  "MSSB_23",
  "MSSB_26",
  "MSSB_29",
  "MSSB_32",
  "MSSB_35",
  "MSSB_38"
)

mssb_negative <- c(
  "MSSB_1",
  "MSSB_4",
  "MSSB_7",
  "MSSB_10",
  "MSSB_13",
  "MSSB_16",
  "MSSB_19",
  "MSSB_22",
  "MSSB_25",
  "MSSB_28",
  "MSSB_31",
  "MSSB_34",
  "MSSB_37"
)

mssb_disorganised <- c(
  "MSSB_3",
  "MSSB_6",
  "MSSB_9",
  "MSSB_12",
  "MSSB_15",
  "MSSB_18",
  "MSSB_21",
  "MSSB_24",
  "MSSB_27",
  "MSSB_30",
  "MSSB_33",
  "MSSB_36"
)
```


OCI-R
```{r}
oci_r_washing <- c(
  "OCI_R_5",
  "OCI_R_11",
  "OCI_R_17"
)

oci_r_obsessing <- c(
  "OCI_R_6",
  "OCI_R_12",
  "OCI_R_18"
)

oci_r_hoarding <- c(
  "OCI_R_1",
  "OCI_R_7",
  "OCI_R_13"
)

oci_r_ordering <- c(
  "OCI_R_3",
  "OCI_R_9",
  "OCI_R_15"
)

oci_r_checking <- c(
  "OCI_R_2",
  "OCI_R_8",
  "OCI_R_14"
)

oci_r_neutralising <- c(
  "OCI_R_4",
  "OCI_R_10",
  "OCI_R_16"
)
```


ASRS

```{r}
asrs_hyper_impuls <- c(
  "ASRS_5",
  "ASRS_6",
  "ASRS_12",
  "ASRS_13",
  "ASRS_14",
  "ASRS_15",
  "ASRS_16",
  "ASRS_17",
  "ASRS_18"
)

asrs_inattentive <- c(
  "ASRS_1",
  "ASRS_2",
  "ASRS_3",
  "ASRS_4",
  "ASRS_7",
  "ASRS_8",
  "ASRS_9",
  "ASRS_10",
  "ASRS_11"
)
```

EAT-26

```{r}
eat_dieting <- c(
  "EAT_1",
  "EAT_6",
  "EAT_7",
  "EAT_10",
  "EAT_11",
  "EAT_12",
  "EAT_14",
  "EAT_16",
  "EAT_17",
  "EAT_22",
  "EAT_23",
  "EAT_24",
  "EAT_26"
)

eat_bul_foodpreoc <- c(
  "EAT_3",
  "EAT_4",
  "EAT_9",
  "EAT_18",
  "EAT_21",
  "EAT_25"
)

eat_oral_ctrl <- c(
  "EAT_2",
  "EAT_5",
  "EAT_8",
  "EAT_13",
  "EAT_15",
  "EAT_19",
  "EAT_20"
)

eat_all_items <- c(
  "EAT_2",
  "EAT_5",
  "EAT_8",
  "EAT_13",
  "EAT_15",
  "EAT_19",
  "EAT_20",
  "EAT_3",
  "EAT_4",
  "EAT_9",
  "EAT_18",
  "EAT_21",
  "EAT_25",
  "EAT_1",
  "EAT_6",
  "EAT_7",
  "EAT_10",
  "EAT_11",
  "EAT_12",
  "EAT_14",
  "EAT_16",
  "EAT_17",
  "EAT_22",
  "EAT_23",
  "EAT_24",
  "EAT_26"
)
```

HCL-32

```{r}
hcl_active <- c(
  "HCL32_2",
  "HCL32_3",
  "HCL32_4",
  "HCL32_5",
  "HCL32_6",
  "HCL32_10",
  "HCL32_11",
  "HCL32_12",
  "HCL32_13",
  "HCL32_15",
  "HCL32_16",
  "HCL32_19",
  "HCL32_20",
  "HCL32_22",
  "HCL32_24",
  "HCL32_28"
)

hcl_irritable <- c(
  "HCL32_7",
  "HCL32_8",
  "HCL32_9",
  "HCL32_21",
  "HCL32_25",
  "HCL32_26",
  "HCL32_27",
  "HCL32_31",
  "HCL32_32"
)
```

STAI
```{r}
STAI_state <- c(
  "STAI_state_1",
  "STAI_state_2",
  "STAI_state_3",
  "STAI_state_4",
  "STAI_state_5",
  "STAI_state_6",
  "STAI_state_7",
  "STAI_state_8",
  "STAI_state_9",
  "STAI_state_10",
  "STAI_state_11",
  "STAI_state_12.quantised",
  "STAI_state_13.quantised",
  "STAI_state_12",
  "STAI_state_13",
  "STAI_state_14",
  "STAI_state_15",
  "STAI_state_16",
  "STAI_state_17",
  "STAI_state_18",
  "STAI_state_19",
  "STAI_state_20")

STAI_trait <- c(
  "STAI_trait_21",
  "STAI_trait_22",
  "STAI_trait_23",
  "STAI_trait_24",
  "STAI_trait_25",
  "STAI_trait_26",
  "STAI_trait_27",
  "STAI_trait_28",
  "STAI_trait_29",
  "STAI_trait_30",
  "STAI_trait_31",
  "STAI_trait_32",
  "STAI_trait_33",
  "STAI_trait_34",
  "STAI_trait_35",
  "STAI_trait_36",
  "STAI_trait_37",
  "STAI_trait_38",
  "STAI_trait_39",
  "STAI_trait_30"
)
```

Create a name dictionary to use for clean naming in plots and tables:
```{r}
name_dict <- c(
  mwq_total_score = "MWQ (mind-wandering)",
  ASRS_total_score = "ASRS (ADHD)", 
  MSSB_total = "MSS-B (schizotypy)",
  AQ_total_score = "AQ (autism spectrum)",
  OCI_R_total_score = "OCI-R (OCD)",
  BDI_shorten_total_score = "BDI short (depression)",
  HCL32_total_score = "HCL-32 (hypomania)",
  EAT_total_score = "EAT (eating disorder)",
  ASRS_hyper_impulse = "ASRS - hyperactive, impulsive",
  ASRS_inattentive = "ASRS - inattentive",
  MSSB_positive = "MSS-B - positive",
  MSSB_negative = "MSS-B - negative",
  MSSB_disorganised = "MSS-B - disorganised",
  OCI_R_hoard = "OCI-R - hoarding",
  OCI_R_wash = "OCI-R - washing",
  OCI_R_obsess = "OCI-R - obsessing",
  OCI_R_order = "OCI-R - ordering",
  OCI_R_check = "OCI-R - checking", 
  OCI_R_neutral = "OCI-R - neutralizing",
  HCL32_act = "HCL-32 - active/elated",
  HCL32_irrit = "HCL-32 - risk-taking/irritable",
  EAT_diet = "EAT - dieting",
  EAT_bul_foodpreoc = "EAT - bulimia, food preoc.",
  EAT_oral_ctrl = "EAT - oral control",
  STAI_trait_total = "STAI - Trait (anxiety)"
)
```


# Overview

For the final data pre-processing, the following steps are executed:

- Import raw merged dataframe received from Bianka
- Filter out observations (no MWQ, missing majority questionnaires, missing BDI, duplicated observations per participant)
- Determine data collection round and medicated/diagnosed participants
- Rename original/Bianka's total scores; create Miha's total scores and compare
- Import EAT raw scores and calculate total scores
- Compare individual item scores in original merged dataframe and EAT scores only dataframe


# Preprocessing

Import raw merged dataset

```{r}
df_merged_raw_dec9 <- read_csv("/Users/Intragalactic/Documents/PhD ELTE/Year 2/Lab/MW spectrum study/MW_spectrum_data/Merged_dataset/all_spectrum_dataset.csv")
```

Create a duplicate for cleaning
```{r}
df_merged_clean_dec9 <- df_merged_raw_dec9
```

**Total number of entries in the complete merged dataset is: 709**

Filter out rows where MWQ has no entries.

```{r}
df_merged_clean_dec9 <- df_merged_clean_dec9 %>%
  filter(!is.na(mwq_1))

nrow(df_merged_clean_dec9)
```

237 participants/rows/obervations were deleted as they lack MWQ responses.

**Remaining after this step: 472**

There seem to be quite a few observations/participants, where majority of questionnaires were not answered. Since this would be impossible to impute, I suggest this rows/observations are deleted from the dataset.

```{r}
df_merged_clean_dec9 <- df_merged_clean_dec9 %>%
  filter(!is.na(MSSB_1) & !is.na(OCI_R_1) & !is.na(AQ_1) & !is.na(EAT_1) & !is.na(HCL32_1))

df_merged_clean
```

**After filtering observations where majority of questionnaires were NA:** - **451 remain** - **21 observations were deleted**

Clean/remove redundant columns:

```{r}
df_merged_clean_dec9 <- df_merged_clean_dec9 %>%  
  dplyr::select(-(c("...1", "X.1", "X.x", "X.y")))
```

```{r}
colnames(df_merged_clean_dec9)
```


Rename all of Bianka's columns to _bianka, so I will be able to precisely compare the scores.
```{r}
df_merged_clean_dec9 <- df_merged_clean_dec9 %>%
  rename(MSSB_total_score_bianka = MSSB_total_score,
         MSSB_pos_bianka = MSSB_pos,
         MSSB_neg_bianka = MSSB_neg,
         MSSB_dis_bianka = MSSB_dis,
         
         OCI_R_total_score_bianka = OCI_R_total_score,
         OCI_R_hoarding_bianka = OCI_R_hoarding,
         OCI_R_washing_bianka = OCI_R_washing,
         OCI_R_obsessing_bianka = OCI_R_obsessing,
         OCI_R_ordering_bianka = OCI_R_ordering,
         OCI_R_neutralizing_bianka = OCI_R_neutralizing,
         OCI_R_checking_bianka = OCI_R_checking,
         
         AQ_total_score_bianka = AQ_total_score,
         
         ASRS_total_score_bianka = ASRS_total_score,
         ASRS_hyperactivity_bianka = ASRS_hyperactivity,
         ASRS_attention_bianka = ASRS_attention,
         
         BDI_shorten_total_score_bianka = BDI_shorten_total_score,
         
         EAT_total_score_bianka = EAT_total_score,
         EAT_dieting_bianka = EAT_dieting,
         EAT_bulimia_bianka = EAT_bulimia,
         EAT_oral_control_bianka = EAT_oral_control,
         
         HCL32_total_score_bianka = HCL32_total_score,
         HCL32_active_bianka = HCL32_active,
         HCL32_irritable_bianka = HCL32_irritable,
         
         mwq_total_score_bianka = mwq_total_score,
         
         RRS_total_score_bianka = RRS_total_score,
         
         CAMSR_total_score_bianka = CAMSR_total_score,
         
         STAI_state_sum_bianka = STAI_state_sum,
         STAI_trait_sum_bianka = STAI_trait_sum
         )
```


I noticed that for many participants `MSSB_total_score` is missing, but they have raw values. Maybe one calculation did not happen. Let's re-calculate total MSSB scores.

```{r}
df_merged_clean_dec9 <- df_merged_clean_dec9 %>%
  mutate(MSSB_total_score_miha = rowSums(across(all_of(mssb_items)), na.rm = TRUE))
```



Perform my scale and subscale calculations for score comparison
```{r}
df_merged_clean_dec9_both_calc <- df_merged_clean_dec9 %>%
  mutate(mwq_total_score_miha          = rowSums(across(all_of(mwq_items))),
            
         MSSB_total_score_miha         = rowSums(across(all_of(mssb_items))),
         MSSB_pos_miha                 = rowSums(across(all_of(mssb_positive))),
         MSSB_neg_miha                 = rowSums(across(all_of(mssb_negative))),
         MSSB_dis_miha                 = rowSums(across(all_of(mssb_disorganised))),
            
         OCI_R_total_score_miha        = rowSums(across(all_of(ocir_items))),
         OCI_R_hoarding_miha           = rowSums(across(all_of(oci_r_hoarding))),
         OCI_R_washing_miha            = rowSums(across(all_of(oci_r_washing))),
         OCI_R_obsessing_miha          = rowSums(across(all_of(oci_r_obsessing))),
         OCI_R_ordering_miha           = rowSums(across(all_of(oci_r_ordering))),
         OCI_R_neutralizing_miha       = rowSums(across(all_of(oci_r_neutralising))),
         OCI_R_checking_miha           = rowSums(across(all_of(oci_r_checking))),
            
         AQ_total_score_miha          = rowSums(across(all_of(aq_items))),
            
         ASRS_total_score_miha         = rowSums(across(all_of(asrs_items))),
         ASRS_hyperactivity_miha       = rowSums(across(all_of(asrs_hyper_impuls))),
         ASRS_attention_miha           = rowSums(across(all_of(asrs_inattentive))),
         
         BDI_shorten_total_score_miha  = rowSums(across(all_of(bdi_items))),
       
         EAT_total_score_miha          = rowSums(across(all_of(eat_items))),
         EAT_dieting_miha              = rowSums(across(all_of(eat_dieting))),
         EAT_bulimia_miha              = rowSums(across(all_of(eat_bul_foodpreoc))),
         EAT_oral_control_miha         = rowSums(across(all_of(eat_oral_ctrl))),
       
         HCL32_total_score_miha        = rowSums(across(all_of(hcl_items))),
         HCL32_active_miha             = rowSums(across(all_of(hcl_active))),
         HCL32_irritable_miha          = rowSums(across(all_of(hcl_irritable))),
       
         STAI_state_sum_miha           = rowSums(across(all_of(STAI_state)), na.rm = TRUE),
         STAI_trait_sum_miha           = rowSums(across(all_of(STAI_trait))))
```

Check is NAs in Bianka's and my calculations match:
```{r}
df_merged_clean_dec9_both_calc %>%
  summarise(across(contains("total_score"), ~ sum(!is.na(.x)))) %>%
  t()

df_merged_clean_dec9_both_calc %>%
  summarise(across(contains("_sum_"), ~ sum(!is.na(.x)))) %>%
  t()
```

Check if scores match
```{r}
df_merged_clean_dec9_both_calc %>%
  summarise(total_cases = n(),
            mwq_match              = sum(mwq_total_score_bianka == mwq_total_score_miha, na.rm = TRUE),
            
            aq_match               = sum(AQ_total_score_bianka == AQ_total_score_miha, na.rm = TRUE),
            
            asrs_match             = sum(ASRS_total_score_bianka == ASRS_total_score_miha, na.rm = TRUE),
            asrs_hyperactive_match = sum(ASRS_hyperactivity_bianka == ASRS_hyperactivity_miha, na.rm = TRUE),
            asrs_inattentive_match = sum(ASRS_attention_bianka == ASRS_attention_miha, na.rm = TRUE),
            
            bdi_match              = sum(BDI_shorten_total_score_bianka == BDI_shorten_total_score_miha, na.rm = TRUE),
            
            mssb_match             = sum(MSSB_total_score_bianka == MSSB_total_score_miha, na.rm = TRUE),
            mssb_pos_match         = sum(MSSB_pos_bianka == MSSB_pos_miha, na.rm = TRUE),
            mssb_neg_match         = sum(MSSB_neg_bianka == MSSB_neg_miha, na.rm = TRUE),
            mssb_dis_match         = sum(MSSB_dis_bianka == MSSB_dis_miha, na.rm = TRUE),
            
            hcl_match              = sum(HCL32_total_score_bianka == HCL32_total_score_miha, na.rm = TRUE),
            hcl_act_match          = sum(HCL32_active_bianka == HCL32_active_miha, na.rm = TRUE),
            hcl_irr_match          = sum(HCL32_irritable_bianka == HCL32_irritable_miha, na.rm = TRUE),
            
            oci_match              = sum(OCI_R_total_score_bianka == OCI_R_total_score_miha, na.rm = TRUE),
            oci_hoard_match        = sum(OCI_R_hoarding_bianka == OCI_R_hoarding_miha, na.rm = TRUE),
            oci_wash_match         = sum(OCI_R_washing_bianka == OCI_R_washing_miha, na.rm = TRUE),
            oci_obsess_match       = sum(OCI_R_obsessing_bianka == OCI_R_obsessing_miha, na.rm = TRUE),
            oci_order_match        = sum(OCI_R_ordering_bianka == OCI_R_ordering_miha, na.rm = TRUE),
            oci_neutral_match      = sum(OCI_R_neutralizing_bianka == OCI_R_neutralizing_miha, na.rm = TRUE),
            oci_check_match        = sum(OCI_R_checking_bianka == OCI_R_checking_miha, na.rm = TRUE),
            
            eat_diet_match         = sum(EAT_dieting_bianka == EAT_dieting_miha, na.rm = TRUE),
            eat_bulimia_match      = sum(EAT_bulimia_bianka == EAT_bulimia_miha, na.rm = TRUE),
            eat_oral_ctrl_match    = sum(EAT_oral_control_bianka == EAT_oral_control_miha, na.rm = TRUE),
            
            STAI_state_match       = sum(STAI_state_sum_bianka == STAI_state_sum_miha, na.rm = TRUE),
            STAI_trait_match       = sum(STAI_trait_sum_bianka == STAI_trait_sum_miha, na.rm = TRUE)) %>%
  t()
```

I also ask uncle ChatGPT how to make code cleaner
```{r}
df_merged_clean_dec9_both_calc %>%
  summarise(
    total_cases = n(),
    across(
      ends_with("_bianka"),
      ~ {
        miha_col <- str_replace(cur_column(), "_bianka$", "_miha")
        
        if (miha_col %in% names(df_merged_clean_dec9_both_calc)) {
          sum(.x == df_merged_clean_dec9_both_calc[[miha_col]], na.rm = TRUE)
        } else {
          NA_integer_  # or 0 if you prefer
        }
      },
      .names = "{str_replace(.col, '_bianka$', '')}_match"
    )
  ) %>%
  t()
```


Good, in all cases where Bianka has all calculations and I have all calculations we match, expect for EAT scores, evidently. So let's calculate those again. 


# Re-calculate EAT scores and compare to previous calculations

## Raw data calculation

Import data
```{r}
eat_scores_raw <- read_csv("/Users/Intragalactic/Documents/PhD ELTE/Year 2/Lab/MW spectrum study/MW_spectrum_data/eat2.csv")
```

Recoding the items
```{r}
recode_eat1 <- paste0("EAT_", c(1:25))
recode_eat2 <- paste0("EAT_", 26)

# 1–25.items
eat_scores_raw_recoded <- eat_scores_raw %>%
  mutate(across(all_of(recode_eat1), ~ case_when(
    . == 1 ~ 3,
    . == 2 ~ 2,
    . == 3 ~ 1,
    . %in% c(4, 5, 6) ~ 0,
    TRUE ~ NA_real_
  )))

eat_scores_raw_recoded <- eat_scores_raw_recoded %>%
  # 26. item
  mutate(across(all_of(recode_eat2), ~ case_when(
    . %in% c(1, 2, 3) ~ 0,
    . == 4 ~ 1,
    . == 5 ~ 2,
    . == 6 ~ 3,
    TRUE ~ NA_real_
  )))

```

Match IDs in both datasets
```{r}
ids_in_both_datasets <- intersect(eat_scores_raw_recoded$Participant.Public.ID, df_merged_clean_dec9_both_calc$Participant.Public.ID)
```


```{r}
eat_scores_raw_recoded <- eat_scores_raw_recoded  %>%
  mutate(EAT_total_recalc = rowSums(across(all_of(eat_all_items)))) %>%
  mutate(EAT_diet_recalc = rowSums(across(all_of(eat_dieting)))) %>%
  mutate(EAT_bul_foodpreoc_recalc = rowSums(across(all_of(eat_bul_foodpreoc)))) %>%
  mutate(EAT_oral_ctrl_recalc = rowSums(across(all_of(eat_oral_ctrl))))
```

Filter those participants who are in both datasets:

```{r}
eat_scores_raw_recoded_filtered <- eat_scores_raw_recoded %>%
  filter(Participant.Public.ID %in%ids_in_both_datasets) %>%
  arrange(Participant.Public.ID) %>%
  filter(!is.na(EAT_25))
```


Extract data from "my" organised dataset
```{r}
df_merged_clean_dec9_both_calc_filtered <- df_merged_clean_dec9_both_calc %>%
  filter(Participant.Public.ID %in% ids_in_both_datasets) %>%
  dplyr::select(c("Participant.Public.ID", starts_with("EAT_"))) %>%
  arrange(Participant.Public.ID)
```


Check if raw items match:
```{r}
df_merged_clean_dec9_both_calc_filtered %>%
  summarise(
    across(
      all_of(eat_items),
      ~ sum(.x == eat_scores_raw_recoded_filtered[[cur_column()]], na.rm = TRUE),
      .names = "{.col}_match"
    )
  ) %>%
  t()
```

Ok, it appears that values of each EAT item match, probably something went wrong in the total score calculation. 

```{r}
sum(df_merged_clean_dec9_both_calc_filtered$EAT_total_score_bianka == eat_scores_raw_recoded_filtered$EAT_total_recalc)
```

```{r}
sum(df_merged_clean_dec9_both_calc_filtered$EAT_total_score_miha == eat_scores_raw_recoded_filtered$EAT_total_recalc)
```

It seems that if we consider new total score calculation in EAT raw data questionnaire, they amtch my calculations in total dataframe. Let's check for individual subscales:
```{r}
sum(df_merged_clean_dec9_both_calc_filtered$EAT_dieting_miha == eat_scores_raw_recoded_filtered$EAT_diet_recalc)
sum(df_merged_clean_dec9_both_calc_filtered$EAT_bulimia_miha == eat_scores_raw_recoded_filtered$EAT_bul_foodpreoc_recalc)
sum(df_merged_clean_dec9_both_calc_filtered$EAT_oral_control_miha == eat_scores_raw_recoded_filtered$EAT_oral_ctrl_recalc)
```
My calculations in original dataframe match re-calculations in the EAT raw dataframe. So, I don't even have to merge the data, because it appears that I can just keep the scores that I calculated. 


# Finalising the dataset

Ok, so it appears that my EAT calculations were OK, and we can work with them in the analysis. Now let's finalise pre-processing of the dataset:

- remove 1 duplicated individual observations
- remove 1 observation with BDI = NA
- change column names
- save relevant column names

So total preprocessing data deletion:

- 237 participants/rows/obervations were deleted as they lack MWQ responses
- 21 observations were deleted due to majority of questionnaires missing 
- 1 observation deleted due to missing BDI 
- 1 observation deleted due to duplicated value for participant 49oe8na4

```{r}
cols_to_keep <- c(
"Participant.Public.ID",
"gender.quantised",
"age.year",

"mwq_total_score_miha",

"AQ_total_score_miha",
"AQ_group",

"ASRS_total_score_miha",
"ASRS_hyperactivity_miha",
"ASRS_attention_miha",

"BDI_shorten_total_score_miha",

"EAT_total_score_miha",
"EAT_dieting_miha",
"EAT_bulimia_miha",
"EAT_oral_control_miha",

"HCL32_total_score_miha",
"HCL32_active_miha",
"HCL32_irritable_miha",
"HCL32_group",

"MSSB_total_score_miha",
"MSSB_pos_miha",
"MSSB_neg_miha",
"MSSB_dis_miha",

"OCI_R_total_score_miha",
"OCI_R_hoarding_miha",
"OCI_R_washing_miha",
"OCI_R_obsessing_miha",
"OCI_R_ordering_miha",
"OCI_R_neutralizing_miha",
"OCI_R_checking_miha",
"OCI_R_group",

"STAI_state_sum_miha",
"STAI_trait_sum_miha"
)
```

Final cleaning
```{r}
df_dec9_final_clean <- df_merged_clean_dec9_both_calc %>%
  filter(!is.na(BDI_shorten_total_score_miha)) %>%
  group_by(Participant.Public.ID) %>%
  slice(1) %>%
  ungroup() %>%
  select(all_of(cols_to_keep)) %>%
  rename_with(~ str_replace(.x, "_miha$", "")) %>%
  rename(gender = gender.quantised,
         age = age.year,
         MWQ_total_score = mwq_total_score,
         STAI_state_total_score = STAI_state_sum,
         STAI_trait_total_score = STAI_trait_sum)
```


Export data:
```{r}
write_csv(df_dec9_final_clean, "df_dec9_final_clean.csv")
```

